DisCon Speaker Change Adult with Preference Analysis

### 2019-01-18 analysis/01_adult_speakerchange_preference.Rmd
add model to adult speaker change experiment

#Pilot 1 data
```{r data preprocessing}
# Data pre-processing

@@

write.csv(data, file="../data/01_adult_speakerchange_preference.data.csv")
data <- read_csv(file="../data/01_adult_speakerchange_preference.data.csv")
```

```{r}
data_ip <- data %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))
```

```{r sanity checks}
data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data <- data %>%
  filter(!workerid %in% drop)
```
```{r}

sample_size <- data %>%
  distinct(workerid, .keep_all = TRUE)

sample_size %>%
 group_by(experiment) %>%
 summarise(n = n())
```

```{r plot1}
plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, speakerChange) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
  group_by(distribution, item, speakerChange) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~speakerChange, 
             labeller = as_labeller(c(change = "speaker change", same = "no change"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")

plot3 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, speakerChange) %>%
  summarise(correct = mean(correct_target1)) %>%
  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
  group_by(distribution, item, speakerChange)

@@

```
```{r wilcoxon test}
## Wilcoxon tests against chance
library(exactRankTests)

data %>%
  filter(phase == "test") %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(distribution) %>%
  mutate(mean= mean(unlist(correct)),
         stat = wilcox.exact(unlist(correct), mu = 0.5)$statistic,
         p = wilcox.exact(unlist(correct), mu = 0.5)$p.value) %>%
  select(distribution,mean,stat,p) %>%
  knitr::kable(digits = 3)
```

>>>>

# Data for speaker change with preference framing
```{r data preprocessing}
# Data pre-processing

@@

#write.csv(data, file="../data/01_adult_speakerchange_preference.data.csv")

data <- read_csv(file="../data/01_adult_speakerchange_preference.data.csv")
```

## Cleaning data

Remove participants who perform below cut-off in training and who participated

```{r sanity checks}
drop_train <- data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data <- data %>%
  distinct(workerid, trial, slide, .keep_all = TRUE)%>%
  filter(!workerid %in% drop_train)
```
## Sample size

```{r}
data %>%
  filter(phase=="test")%>%
  group_by(speakerChange)%>%
  summarise(N = length(unique(workerid)),
            datapoints = n())

```

# Plotting performance by condition

```{r plot1}
plot3 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, speakerChange) %>%
  summarise(correct = mean(correct_target1)) %>%
  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
  group_by(distribution, item, speakerChange)

@@

```

# Comparison to chance in each condition

```{r wilcoxon test}
## Wilcoxon tests against chance
library(exactRankTests)

data %>%
  filter(phase == "test") %>%
  group_by(speakerChange, workerid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(speakerChange) %>%
  mutate(mean= mean(unlist(correct)),
         stat = wilcox.exact(unlist(correct), mu = 1/3)$statistic,
         p = wilcox.exact(unlist(correct), mu = 1/3)$p.value) %>%
  select(speakerChange,mean,stat,p) %>%
  knitr::kable(digits = 3)
```

# Model

```{r Bayesian}
library(brms)

model_data <- data%>%
  filter(phase == "test")

#   model

bm1 <- readRDS("../saves/01_adult_speakerchange_model_bm1.rds")

brm(correct_target1 ~ speakerChange +
                      (speakerChange | workerid) + (speakerChange | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

saveRDS(bm1, "../saves/01_adult_speakerchange_model_bm1.rds")

```

## Plot model predictors

```{r}
bayesplot::mcmc_areas(as.array(bm1), pars = c("b_Intercept", "b_speakerChangesame"), prob = 0.95)+
  geom_vline(xintercept = 0, lty = 2, col = "black")+
  theme_few()
```

## Model comparison

```{r}
# model comparison
# reduced model

bm2 <- readRDS("../saves/01_adult_speakerchange_model_bm2.rds")

bm2 <- brm(correct_target1 ~ 1 +
                      (speakerChange | workerid) + (speakerChange | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

saveRDS(bm2, "../saves/01_adult_speakerchange_model_bm2.rds")

# WAIC scores

child_waic <- brms::WAIC(bm1, bm2, compare = F)

child_weights <- model_weights(bm1, bm2)

# Bayes Factors (slightly variable)
bf_full_null <- bayes_factor(bm1, bm2, log = FALSE, maxiter = 5000)

```
## Model comparison using WAIC and Bayes Factor
```{r}
data_frame(
  model = c("bm1_w_condition","bm2"),
  WAIC = c(child_waic$bm1$estimates[3,1],child_waic$bm2$estimates[3,1]),
  SE = c(child_waic$bm1$estimates[3,2],child_waic$bm2$estimates[3,2]),
  weight = c(child_weights[1],child_weights[2]),
  BF_bm1_bm2 = c(round(bf_full_null$bf,2),"-"))%>%
  kable(digits = 2)
```
